Appeal of rejection of GCB-20-1713

### 2020-09-17 manuscript/journal_submissions/2020_8_GCB/appeal.Rmd
Update appeal.Rmd

**(1) Reviewer 1 provided an inaccurate assessment of the scope of our analysis relative to previous studies.**  The reviewer states, "...the findings seem not improving contemporary knowledge of forest carbon cycling, and the study appears to be a simple statistical analyses of literature data..." and "the analyses performed were too conventional that similar analyses with a smaller size of similar datasets have been performed a decade ago." These statements betray a lack of perspective on the scope of our analysis relative to previous studies. Whereas most studies consider at most a few flux variables, our considers nine. The most comprehensive similar study is @luyssaert_co_2007, which was published in *GCB* more than a decade ago, includes much less data, does not control for effects of stand age/ disturbance history, and examines latitudinal/ global climatic trends in only **#** variables. This study has been cited >580 times and was highlighted as a noteworthy publication within *GCB* ([Long, 2020](https://doi.org/10.1111/gcb.14921)). It would seem that something along these lines, but with an expanded database and a more carefully controlled treatment of forest age and management/disturbance history, would have high potential to become a "classic" reference in global forest carbon cycling.

>>>>

**(1) Reviewer 1 provided an inaccurate assessment of the scope of our analysis relative to previous studies.**  The reviewer states, "...the findings seem not improving contemporary knowledge of forest carbon cycling, and the study appears to be a simple statistical analyses of literature data..." and "the analyses performed were too conventional that similar analyses with a smaller size of similar datasets have been performed a decade ago." These statements betray a lack of perspective on the scope of our analysis relative to previous studies. Whereas most studies consider at most a few flux variables, our considers nine. The most comprehensive similar study is @luyssaert_co_2007, which was published in *GCB* more than a decade ago, includes much less data, does not control for effects of stand age/ disturbance history, and examines latitudinal/ global climatic trends in only 3 variables. This study has been cited >580 times and was highlighted as a noteworthy publication within *GCB* ([Long, 2020](https://doi.org/10.1111/gcb.14921)). It would seem that something along these lines, but with an expanded database and a more carefully controlled treatment of forest age and management/disturbance history, would have high potential to become a "classic" reference in global forest carbon cycling.
